\textbf{Automated Reasoning\\Practical Assignment -- Part 2}

### 2022-12-22 part2/report/paper.tex
Update report

$$\forall_{s = \mathtt{f}(s_1, \dots, s_n)} \forall_{t = \mathtt{g}(t_1, \dots,
t_m)} \succ_{c,st}\ =\ \equiv_{\mathtt{f,g}} \land \bigvee_{\mathtt{EQ},
\varphi \in \mathcal{P}^\mathtt{EQ}_\varphi(n, m)}
\left(
	\bigwedge_{i,\mathtt{EQ}(\varphi(i)) = \bot} \succ_{s_{\varphi(i)},t_i}
	\bigwedge_{i,\mathtt{EQ}(\varphi(i)) = \top} \approx_{s_{\varphi(i)},t_i}
\right)
$$
\subsection{Results}
Running Z3 with all the constraints and variable definitions as given above
provides us with the following ordering: $\mathtt{a \rhd c \rhd f \rhd g \rhd b
\rhd h \rhd d }$. Finding another symbol ordering is rather easy, we just added
the constraint $\mathtt{\neg \rhd_{h,d}}$. This gives us a new symbol ordering:
$\mathtt{a \rhd c \rhd b \equiv f \rhd g \rhd d \rhd h}$.

The human-readable proof for the inequality
$\mathtt{h}(\mathtt{g}(x,\mathtt{g}(u,z)),\mathtt{c}(x,y,x,z)) \rhd
\mathtt{f}(\mathtt{d}(x,z),u)$ given the first ordering is as follows.
By 2b it suffices to proof that $\mathtt{h \rhd d}$ which holds, and
$\mathtt{h}(\mathtt{g}(x,\mathtt{g}(u,z)),\mathtt{c}(x,y,x,z))~\succ~x$, and
$\mathtt{h}(\mathtt{g}(x,\mathtt{g}(u,z)),\mathtt{c}(x,y,x,z))~\succ~z$. Now
these two inequalities trivially follow from recursively applying rule 2a until
a variable $x$ or $z$ is reached inside the arguments of $\mathtt{h}$, using 3a
on the variables completes the proof.

@@

	\begin{tabular}{ll}
		hinted & a puzzle that satisfies the generated constraints\\
		filled & an alternate solution to that puzzle\\
		contributes & places where the count of surrounding black squares differ.
	\end{tabular}

@@

	$$\forall_{r,c}: 0\le \text{hinted}_{r,c} \le 1$$
	$$\forall_{r,c}: 0\le \text{filled}_{r,c} \le 1$$
	$$\forall_{r,c}: 0\le \text{contributes}_{r,c} \le 1$$

@@

	$$\forall_{r,c}: \sum_{\substack{r-1\le r' \le r+1\\c-1\le c'\le c+1}}\text{grid}_{r',c'} = \sum_{\substack{r-1\le r' \le r+1\\c-1\le c'\le c+1}}\text{filled}_{r',c'}\to \text{contributes}_{r,c}=1$$

@@

	$$\sum_{r,c}\text{constributes}_{r,c} = \min_{}(\sum_{r,c}\text{contributes}_{r,c}
	)$$

@@

	$$\exists_{r,c : \text{model}(\text{contributes}_{r,c})=1}: \text{hinted}_{r,c}$$

>>>>

$$\forall_{s = \mathtt{f}(s_1, \dots, s_n)} \forall_{t = \mathtt{g}(t_1, \dots,
t_m)} \succ_{c,st}\ =\ \equiv_{\mathtt{f,g}} \land \bigvee_{\mathtt{EQ},
\varphi \in \mathcal{P}^\mathtt{EQ}_\varphi(n, m)}
\left(
	\bigwedge_{i,\mathtt{EQ}(\varphi(i)) = \bot} \succ_{s_{\varphi(i)},t_i}
	\bigwedge_{i,\mathtt{EQ}(\varphi(i)) = \top} \approx_{s_{\varphi(i)},t_i}
\right)
$$

\subsection{Results}
Running Z3 with all the constraints and variable definitions as given above provides us with the following order: $\mathtt{a \rhd c \equiv d \rhd b \rhd f \equiv h \rhd g}$.
For this order we get the following proof for inequality 3:\\
\begin{tabular}{l|lll}
	Line & Statement & Rule & Children\\
	\hline
	1 & $u \approx u$ & 3a & \\
	2 & $u\succsim u$ & 1 & 1\\
	3 & $x \approx x$ & 3a & \\
	4 & $z \approx z$ & 3a & \\
	5 & $g(u,z) \succ u$ & 2a & 2\\
	6 & $g(u,z) \succsim u$ & 1 & 5\\
	7 & $g(x, g(u, z)) \succ u$ & 2a & 6\\
	8 & $c(x, y, x, z) \succ d(x,z)$ & 2c & $c\equiv d$, 3, 4, $A_2=\{\{x,y\}\}$\\
	9 & $h(g(x, g(u, z)), c(x, y, x, z)) \succ f(d(x, z), u)$ & 2c & $h \equiv f$, 7, 8
\end{tabular}\\
This is the only order for which all inequalities are provable.

% Running Z3 with all the constraints and variable definitions as given above
% provides us with the following ordering: $\mathtt{a \rhd c \rhd f \rhd g \rhd b
% \rhd h \rhd d }$. Finding another symbol ordering is rather easy, we just added
% the constraint $\mathtt{\neg \rhd_{h,d}}$. This gives us a new symbol ordering:
% $\mathtt{a \rhd c \rhd b \equiv f \rhd g \rhd d \rhd h}$.

% The human-readable proof for the inequality
% $\mathtt{h}(\mathtt{g}(x,\mathtt{g}(u,z)),\mathtt{c}(x,y,x,z)) \rhd
% \mathtt{f}(\mathtt{d}(x,z),u)$ given the first ordering is as follows.
% By 2b it suffices to proof that $\mathtt{h \rhd d}$ which holds, and
% $\mathtt{h}(\mathtt{g}(x,\mathtt{g}(u,z)),\mathtt{c}(x,y,x,z))~\succ~x$, and
% $\mathtt{h}(\mathtt{g}(x,\mathtt{g}(u,z)),\mathtt{c}(x,y,x,z))~\succ~z$. Now
% these two inequalities trivially follow from recursively applying rule 2a until
% a variable $x$ or $z$ is reached inside the arguments of $\mathtt{h}$, using 3a
% on the variables completes the proof.

@@

	\begin{tabular}{ll}
		hinted & a puzzle that satisfies the generated constraints\\
		filled & an alternate solution to that puzzle\\
		differs & places where the count of surrounding black squares differ.
	\end{tabular}

@@

	$$\forall_{r,c}: 0\le \text{hinted}_{r,c} \le 1$$
	$$\forall_{r,c}: 0\le \text{filled}_{r,c} \le 1$$
	$$\forall_{r,c}: 0\le \text{differs}_{r,c} \le 1$$

@@

	$$\forall_{r,c}: \sum_{\substack{r-1\le r' \le r+1\\c-1\le c'\le c+1}}\text{grid}_{r',c'} = \sum_{\substack{r-1\le r' \le r+1\\c-1\le c'\le c+1}}\text{filled}_{r',c'}\to \text{differs}_{r,c}=1$$

@@

	$$\sum_{r,c}\text{differs}_{r,c} = \min_{}(\sum_{r,c}\text{differs}_{r,c}
	)$$

@@

	$$\exists_{r,c : \text{model}(\text{differs}_{r,c})=1}: \text{hinted}_{r,c}$$
